---
title: "HW3 R and Rmarkdown"
author: "Courtney Lopez"
date: "2/11/2018"
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Delete this text, and add a few paragraphs of introduction about the NEON project, and the sites you are comparing.

# Methods

Describe briefly where the data came from (information in the pdf file in the data folder) and how you are analyzing them (e.g. using R to visualize the results and an ANOVA to test for significant differences).

# Results

```{r load-in-data}
# read in the litterfall data from a csv
litterfall_data <- read.csv("data/ltr_massdata.csv",
                            header = TRUE)
```


```{r subset-out-HARV-data}
# just look at site 'HARV'
HARV_data <- subset(litterfall_data,
                    siteID == "HARV")
```


```{r boxplot-of-functional-types}
# mass of litter by functional type
boxplot(dryMass ~ functionalGroup,
        data = HARV_data,
        main = "Mass of litterfall by functional group",
        xlab = "Functional Group of Litter",
        ylab = "Dry mass of litter in grams")
```

Add a number of code chunks in the Results section. These should read in, subset, plot (no need to save it to pdf, since it will be put into the rendered docx when you click 'knit'), and run a statistical test on your dataset.

# Discussion

Discuss the results you found. Which sites had the highest amounts of litter mass? The smallest? Why do you think this is so?
